A Two-Infall Star Formation History with Outflows and Radial Migration

### 2025-01-24 src/tex/ms.tex
Updates from Overleaf

\begin{figure*}
    \centering
    \includegraphics{figures/onezone_params.pdf}
    \caption{Abundance tracks in the [O/Fe]--[Fe/H] plane for one-zone chemical evolution models which assume different values for the. Illustration of the effect of changing the infall history parameters on one-zone gas-phase abundances. For consistency, all models use the {\tt yZ1} yield set and assume $\eta=0.4$. (a) The first infall timescale $\tau_1$ adjusts the position and spread of the high-$\alpha$ sequence. (b) The second infall timescale $\tau_2$ adjusts the width of the low-$\alpha$ peak (separation of the low-$\alpha$ peaks) and the width of the MDF. (c) The onset time $t_{\rm on}$ has a minor effect on the position of the abundance distributions for values $t_{\rm on}\ge 3$ Gyr. While the ISM abundance at $t_{\rm on}$ varies widely for some parameter choices, it has a negligible impact on the stellar abundance distributions. Key takeaway: The second infall timescale $\tau_2$ is the most important parameter to fit the low-$\alpha$ sequence and MDF.}
    \label{fig:twoinfall-parameters-low-yields}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \includegraphics{figures/onezone_params.pdf}
    \caption{Gas abundance tracks in the [O/Fe]--[Fe/H] plane for one-zone chemical evolution models which assume different values for the infall history parameters. In each panel, one parameter is varied according to the legend while the other two are held fixed. The open symbols along each curve mark logarithmic steps in time, as denoted in panel (b). The marginal panels show the corresponding stellar abundance distributions, which are convolved with a Gaussian kernel with a width of 0.02 dex for visual clarity. All models use the {\tt yZ1} yield set and assume $\eta=0.4$. {\bf (a)} The first infall timescale $\tau_1$ primarily affects the stellar distribution along the high-$\alpha$ sequence. {\bf (b)} The second infall timescale $\tau_2$ affects the [O/Fe] distribution of the low-$\alpha$ sequence and the width of the MDF. {\bf (c)} The onset time $t_{\rm on}$ has a minor effect on the position of the abundance distributions for values $t_{\rm on}\ge 3$ Gyr. While the ISM abundance at $t_{\rm on}$ varies widely for some parameter choices, it has a negligible impact on the stellar abundance distributions. {\bf Key takeaway:} The second infall timescale $\tau_2$ is the most important parameter to fit the low-$\alpha$ sequence and MDF.}
    \label{fig:twoinfall-parameters-low-yields}
\end{figure*}
